Comparison of Catalogs

### 2024-07-31 compare/compare.qmd
minor fixes x2

In this script we will compare out 2 catalogs @kovlakasHeraklionExtragalacticCatalogue2021 and [@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a]

-   The data have been joined based on their position in the sky (Ra, Dec, Distance).
-   We use TOPCAT to create two joins, an inner and an outer join
-   We will use the inner join for 1-1 comparisons
-   If we see that the data are similar we can use the outer join

@@

-   Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix. It’s like a color chart that shows us how closely related different variables are.

    In a correlation heatmap, each variable is represented by a row and a column, and the cells show the correlation between them. The color of each cell represents the strength and direction of the correlation, with darker colors indicating stronger correlations.

@@

    The function uses the seaborn library to create the histogram and applies a 3-sigma clip if `sigmaclip` is True.
    The histogram is displayed with appropriate labels and titles.
    The statistical information about the input data is returned as a pandas DataFrame.
    """
    plt.close()
    temp_table = QTable()
    temp_table["Percentage change"]= x.copy()

    if sigmaclip is True:
        temp_table["Percentage change, after 3 sigma clip"] = sigma_clip(temp_table["Percentage change"],3)

@@

    sns.histplot(temp_table["Percentage change"], kde = True, label = "Percentage change")

    if sigmaclip is True:
        sns.histplot(temp_table["Percentage change, after 3 sigma clip"], kde = True, label = "Percentage change, after 3 sigma clip")

@@

@@

```{python}
sns.histplot(temp, kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```
:::

@@

## Internal
```{python}
sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
plt.show()
```
Here we can see an attempt to correlate the internal absorption of the two catalogs, however as it is very clear, there is no correlation, since even their distributions are not similar.
:::

@@

It is possible we dont see a good correlation because we dont have a big enough common sample

@@

|      LCV       |  HECATE  |                        Description                        |                    Count                    |
|:----------------:|:----------------:|:----------------:|:----------------:|
|     logM26     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logM26"]`     |
|     logMHI     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logMHI"]`     |
|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |    `{python} non_nan_counts["logM_HEC"]`    |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |    `{python} non_nan_counts["logM_GSW"]`    |
| logStellarMass |          |               Stellar Mass from M\_\*/L=0.6               | `{python} non_nan_counts["logStellarMass"]` |

>>>>

In this script we will compare 2 catalogs @kovlakasHeraklionExtragalacticCatalogue2021 and [@karachentsevUPDATEDNEARBYGALAXY2013, @karachentsevSTARFORMATIONPROPERTIES2013a]

-   The data have been joined based on their position in the sky (Ra, Dec, Distance).
-   We use TOPCAT to create two joins, an inner and an outer join
-   We will use the inner join for 1-1 comparisons
-   If we see that the data are similar we can use the outer join
-   For the comparison we keep the parameters names exactly they are given in the catalogs

@@

    -   Correlation Heatmaps: A correlation heatmap is a graphical tool that displays the correlation between multiple variables as a color-coded matrix. It’s like a color chart that shows us how closely related different variables are. In a correlation heatmap, each variable is represented by a row and a column, and the cells show the correlation between them. The color of each cell represents the strength and direction of the correlation, with darker colors indicating stronger correlations.

@@

    The function uses the seaborn library to create the histogram and applies a 3-sigma clip if `sigmaclip` is True.
    The histogram is displayed with appropriate labels and titles.
    The statistical information about the input data is returned as a pandas DataFrame.
    """
    plt.close()
    temp_table = QTable()
    temp_table["Percentage change [%]"]= x.copy()

    if sigmaclip is True:
        temp_table["Percentage change [%], after 3 sigma clip"] = sigma_clip(temp_table["Percentage change [%]"],3)

@@

    sns.histplot(temp_table["Percentage change [%]"], kde = True, label = "Percentage change [%]")

    if sigmaclip is True:
        sns.histplot(temp_table["Percentage change [%], after 3 sigma clip"], kde = True, label = "Percentage change [%], after 3 sigma clip")

@@

[?] After the sigma clip we only lose 39 galaxies ($14\%$) and we can see that both the median and the mean of the percentage change are close to $0\%$.This is why we can assume that the Types of the galaxies are the same for the two catalogs

@@

```{python}
sns.histplot(temp, kde = True)
plt.title("Percentage change Distribution [%]")
plt.xlabel(f"K band magnitude [{dt['K'].unit}]")
plt.show()
```

[?]
:::

@@

## Internal
```{python}
sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
plt.show()
```
Here we can see an attempt to correlate the internal absorption of the two catalogs, however as it is very clear, there is no correlation, since even their distributions are not similar.
[?]
:::

@@

[?] It is possible we dont see a good correlation because we dont have a big enough common sample

@@

|      LCV       |  HECATE  |                        Description                        |                    Count                    |
|:----------------:|:----------------:|:----------------:|:----------------:|
|     logM26     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logM26"]`     |
|     logMHI     |          |              Log mass within Holmberg radius              |     `{python} non_nan_counts["logMHI"]`     |
|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |    `{python} non_nan_counts["logM_HEC"]`    |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |    `{python} non_nan_counts["logM_GSW"]`    |
| logStellarMass |          |               Stellar Mass from $M_*/L=0.6$               | `{python} non_nan_counts["logStellarMass"]` |
